Clone and graft:\\ Testing scientific applications as they are built

### 2014-12-03 turcksin-spring-mechanics/paper.tex
Provide cross-references within the paper.

Consequently, different approaches are necessary. In the following, we will
lay out what we have learned from building and testing the \aspect{} code for the
geodynamics community over the past few years. In the following, let us first
talk briefly about what \aspect{} does and how the way it is used is
prototypical for scientific codes (Section~\ref{...}). At the same time,
\aspect{} is a very complex code and just installing it is non-trivial;
consequently, it does not serve the purpose of this book well and we will
present a simple model problem and model code in Section~\ref{...} that we
will then use throughout the rest of the chapter. Section~\ref{...} then
discusses how we can write tests alongside developing the code -- using the
\textit{clone and graft} technique of creating test cases. ...COMPLETE...

\section{\aspect{}: the Advanced Solver for Problems in Earth ConvecTion}

@@

Like many academic codes, \aspect{} has no graphical user interface but
instead is driven by input files; it is also designed in such a way that it is
easy to add functionality through plugins, i.e., self-contained source files
that simply implement a class derived from some base class and that is then
registered in \aspect{}'s plugin registry at run time. Because this is the way
users interact with this code, it is also the framework within which we have
to approach testing: tests need to consist of specially crafted input files
and/or plugins.

\section{Make it simple for me: A model problem}

@@

\section{A first program}

@@

\section{Testing for perpetuity}

@@

\section{More functionality}

@@

\section{Practical considerations}

@@

\section{Conclusions}

>>>>

Consequently, different approaches are necessary. In the following, we will
lay out what we have learned from building and testing the \aspect{} code for the
geodynamics community over the past few years. In the following, let us first
talk briefly about what \aspect{} does and how the way it is used is
prototypical for scientific codes (Section~\ref{sec:aspect}). At the same time,
\aspect{} is a very complex code and just installing it is non-trivial;
consequently, it does not serve the purpose of this book well and we will
present a simple model problem and model code in
Sections~\ref{sec:model-problem} and \ref{sec:first-steps} that we
will then use throughout the rest of the chapter. Sections~\ref{sec:testing}
and \ref{sec:extending} then
discuss how we write tests for whole applications, and how this process
happens as we continue to develop the code -- using the
\textit{clone and graft} technique of creating test
cases. Section~\ref{sec:practice} then deals with how real practice interferes
with the ideas discussed in previous sections, and we conclude and summarize
in Section~\ref{sec:conclusions}.

\section{\aspect{}: the Advanced Solver for Problems in Earth ConvecTion}
\label{sec:aspect}

@@

Like many academic codes, \aspect{} has no graphical user interface but
instead is driven by input files; it is also designed in such a way that it is
easy to add functionality through plugins, i.e., self-contained source files
that simply implement a class derived from some base class and that is then
registered in \aspect{}'s plugin registry at run time. Because this is the way
users interact with this code, it is also the framework within which we have
to approach testing: tests need to consist of specially crafted input files
and/or plugins. Plugins go beyond what we can discuss here, but we will show
you that it is actually quite simple to write tests using input files.

\section{Make it simple for me: A model problem}
\label{sec:model-problem}

@@

\section{A first program}
\label{sec:first-steps}

@@

\section{Testing for perpetuity}
\label{sec:testing}

@@

\section{More functionality}
\label{sec:extending}

@@

\section{Practical considerations}
\label{sec:practice}

@@

\section{Conclusions}
\label{sec:conclusions}
